updated_workflow

### 2024-04-12 README.Rmd
updated

### Normalizing values.

@@

First we need to extract a design matrix.

Then we can normalyze the data. 
```{r}
# Extracting design matrix
design_matrix = extract_design_matrix(prepared_data)

# normalyze the data

source("R/normalyze.R")

normalyzed_data = normalyze(prepared_data,design_matrix)
```

@@

Here we use a dixon test from the outliers package to detect outliers from each of our replicates.

```{r}
outliers = handle_outliers(normalyzed_data)
```

@@

```{r}
final_data = add_cleavages(joined_with_library)
```

>>>>

### Loading design matrix

Before we normalyze data, we need to know what samples are in what groups. We can do that by defining a design matrix. 
```{r}
design_matrix = readr::read_csv("annotation.csv")

head(design_matrix)

```
### Normalyzing data

@@

Now we can normalyze the data.
```{r}
normalyzed_data = normalyze(prepared_data,design_matrix)
```

@@

Here we use a dixon test from the outliers package to detect outliers from each of our replicates. We need to know what samples are part of which groups, so we need to specify the design matrix here too. Make sure that the column header names are "sample" and "group" just like before.

```{r}
design_matrix = readr::read_csv("annotation.csv")
outliers = handle_outliers(normalyzed_data,design_matrix)
```

@@

```{r}
final_data = add_cleavages(joined_with_library)

head(final_data)
```
